---
title: "COVID-19 Dashboard"
author: "Vivian chiou"
# date: "May 13, 2020"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    # vertical_layout: scroll
    social: menu
    # source_code: embed
    # css: styles.css
    
runtime: shiny

---

```{r setup, echo = FALSE, include=FALSE}
# packages = c("dplyr", "shiny", "shinymaterial", "plotly", "viridisLite", "tidyverse", "shinyWidgets", "DT", "RColorBrewer", "shinyjs", "leaflet", "leaflet.extras", "scales")
# ipak <- function(pkg){
#   new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
#   if (length(new.pkg)) 
#     install.packages(new.pkg, dependencies = TRUE)
#   sapply(pkg, library, character.only = TRUE)
# }
# ipak(packages)

library(flexdashboard)
library(shiny)
library(leaflet)
library(RColorBrewer)
library(rtweet)
library(rmarkdown)
library(styler)
library(revealjs)
library(htmlwidgets)
library(digest)
library(bit)
library(ggplot2)
library(rlist)
# library(knitr)
library(evaluate)
library(leafpop)
library(widgetframe)
library(data.table)
library(dplyr)
library(highcharter)
library(janitor)
library(htmltools)
library(DT)
library(plotly)
library(leaflet.extras)
library(leafpop)
library(purrr)
library(stringi)
 # library(httr)
# library(coronavirus)
# library(covid19italy)
```



```{r}
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"
```


```{r global, include=FALSE}

raw_data <- read.csv("data/covid_19_data.csv", stringsAsFactors = FALSE)

covid_19_data <- raw_data %>% janitor::clean_names() %>%
  mutate(date = as.Date(raw_data$ObservationDate, format = "%m/%d/%y"))

Last_update_date = max(covid_19_data$date)
  
covid_19_data_latest <- covid_19_data %>%
  filter(observation_date %in% max(covid_19_data$observation_date))%>%
  mutate(total_confirmed = sum(confirmed),
            total_recovered = sum(recovered),
            total_deaths = sum(deaths),
         total_active = total_confirmed - total_recovered - total_deaths)

total_confirmed <- sum(covid_19_data$confirmed)
total_recovered <- sum(covid_19_data$recovered) 
total_deaths <- sum(covid_19_data$deaths) 
total_active <- total_confirmed - total_recovered - total_deaths

date_total <- covid_19_data %>%
  group_by(date) %>%
  summarise(total_confirmed = sum(confirmed),
            total_recovered = sum(recovered),
            total_deaths = sum(deaths))%>%
  mutate(total_active = total_confirmed - total_recovered - total_deaths)

country_total <- covid_19_data %>%
  group_by(country_region) %>%
  summarise(total_confirmed = sum(confirmed),
            total_recovered = sum(recovered),
            total_deaths = sum(deaths))%>%
  mutate(total_active = total_confirmed - total_recovered - total_deaths)

date_list = covid_19_data$date %>% unique()
country_list = covid_19_data$country_region %>% unique()

data(worldgeojson, package = "highcharter")

# data clean
df1 = covid_19_data
df1$country_region[df1$country_region == "Mainland China"] = "China"
df1$country_region[df1$country_region == "US"] = "United States of America"

# df2 <- df1 %>%
#   group_by(date) %>%


```

DashBoard
=======================================================================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------
hi!

My Data Source from kaggle : sudalairajkumar/novel-corona-virus-2019-dataset

Data Update At :

`r Last_update_date`

** Context from kagggle

From World Health Organization - On 31 December 2019, WHO was alerted to several cases of pneumonia in Wuhan City, Hubei Province of China. The virus did not match any other known virus. This raised concern because when a virus is new, we do not know how it affects people.

So daily level information on the affected people can give some interesting insights when it is made available to the broader data science community.

Johns Hopkins University has made an excellent dashboard using the affected cases data. Data is extracted from the google sheets associated and made available here.

Edited:
Now data is available as csv files in the Johns Hopkins Github repository. Please refer to the github repository for the Terms of Use details. Uploading it here for using it in Kaggle kernels and getting insights from the broader DS community.

row { data-height = 100 }
-----------------------------------------------------------------------

### `r paste(icon("arrow-up"), "Confirmed Cases :", prettyNum(max(covid_19_data_latest$total_confirmed), big.mark = ","))`

```{r}
flexdashboard::valueBox(prettyNum(total_confirmed, big.mark = ","),
         color = "danger", icon = "fa-users")
```

### `r paste(icon("percent"), "of Active Cases :", round(total_active*100/total_confirmed, digits = 0), "%")`

```{r}
flexdashboard::valueBox(prettyNum(total_active, big.mark = ","),
         color = "primary", icon = "fa-chart-line")
```

### `r paste(icon("percent"), "of Recovered Cases :", round(total_recovered*100/total_confirmed, digits = 0), "%")`

```{r}
flexdashboard::valueBox(prettyNum(total_recovered, big.mark = ","),
         color = "primary", icon = "fa-stethoscope")
```

### `r paste(icon("percent"), "of Deaths Cases :", round(total_deaths*100/total_confirmed, digits = 0), "%")`

```{r}
flexdashboard::valueBox(prettyNum(total_deaths, big.mark = ","),
         color = "danger", icon = "fa-heartbeat")
```

row { data-height = 200 }
-----------------------------------------------------------------------

### 

```{r}
# hc_theme_gridlight() hc_theme_economist()  hc_theme_538()
country_total %>%
  arrange(desc(total_confirmed)) %>% 
  head(6) %>%
  hchart("bar",hcaes(x = country_region,  y = total_confirmed )) %>%
  hc_title(text = "Top 10 country of total_confirmed ") %>%
  hc_add_theme(hc_theme_economist())

```

### 

```{r}

date_total %>%
  hchart("line",hcaes(x = date, y = total_confirmed)) %>%
  hc_title(text = "Trendline of COVAID-19 confirmed") %>%
  hc_add_theme(hc_theme_economist())

```


row { data-height = 300 }
-----------------------------------------------------------------------

### 
```{r}
plot_data1 = country_total %>%
  arrange(desc(total_confirmed)) %>% 
  head(15)

plotly::plot_ly(data = plot_data1, 
                x = ~ country_region, 
                y = ~ log(total_active), 
                type = "bar", 
                name = "Active",
                marker = list(color = "#1f77b4")) %>%
  plotly::add_trace(y = ~ log(total_recovered), 
                    name = "Recovered",
                    marker = list(color = "forestgreen")) %>%
  plotly::add_trace(y = ~ log(total_deaths), 
                    name = "Death",
                    marker = list(color = "red")) %>%
  plotly::layout(title = "",
                 barmode = 'stack',
                 yaxis = list(title = "Total Cases (log scaled)",
                              type = "log"),
                 xaxis = list(title = "", categoryarray=unique(plot_data1$total_active)),
                 hovermode = "compare",
                 annotations = list(
                   text = "",
                   xref = "paper",
                   yref = "paper",
                   showarrow = FALSE,
                  x = 0.95,
                  y = 1
                 ),
                 margin =  list(
                   # l = 60,
                   # r = 40,
                   b = 10,
                   t = 10,
                   pad = 2
                 ))



```


Trend
=======================================================================

<!-- Column {.sidebar} -->
<!-- ----------------------------------------------------------------------- -->

<!-- hi! -->

Column 
-----------------------------------------------------------------------

### Global Daily Cumulative Cases by Type
    
```{r}
plotly::plot_ly(data = date_total,
                x = ~ date,
                y = ~ total_active, 
                name = 'Active', 
                fillcolor = active_color,
                type = 'scatter',
                mode = 'none', 
                stackgroup = 'one') %>%
  plotly::add_trace(y = ~ total_recovered,
                    name = "Recovered",
                    fillcolor = recovered_color) %>%
  plotly::add_trace(y = ~ total_deaths,
                    name = "Death",
                    fillcolor = death_color) %>%
  plotly::layout(title = "",
                 yaxis = list(title = "Cumulative Number of Cases"),
                 xaxis = list(title = ""),
                 legend = list(x = 0.1, y = 0.9),
                 hovermode = "compare")
  
```


### New Cases - Top 15 Countries (`r  Last_update_date`)

```{r new_cases}

covid_19_data_latest %>%
  group_by(country_region) %>%
  summarise(total_cases = sum(confirmed)) %>%
  arrange(desc(total_cases)) %>% 
  head(10) %>%
  plotly::plot_ly(x = ~ country_region,
                  y = ~ total_cases,
                  text = ~ total_cases,
                  textposition = 'auto',
                  type = "bar") %>%
  plotly::layout(yaxis = list(title = "Number of Cases"),
                 xaxis = list(title = ""),
                 # xaxis = list(title = "", categoryarray=unique(covid_19_data_latest$total_cases)),
                 margin =  list(
                   # l = 10,
                   # r = 10,
                   b = 10,
                   t = 10,
                   pad = 2
                 ))

```

Column {data-width=600}
-------------------------------------

### Trajectory Plot - Major Countries 

```{r}
covid_19_data_latest %>% 
  janitor::clean_names() %>% 
  filter(!country_region %in% 'Others') %>% 
  group_by(country_region) %>% 
  summarise(total_confirmed = sum(confirmed)) %>% 
  filter(total_confirmed > 0) %>% 
  mutate(log_total_confirmed = log(total_confirmed)) -> countries

highchart() %>%
  hc_add_series_map(worldgeojson, countries, value = 'log_total_confirmed', joinBy = c('name','country_region'))  %>% 
  #hc_colors(c("darkorange", "darkgray")) %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_title(text = "Countries with nCov exposure") %>% 
  hc_subtitle(text = 'with Log of Total Confirmed') 
```


### Recovery and Death Rates for Countries with at Least 10000 Cases

```{r}
covid_19_data_latest %>% 
  janitor::clean_names() %>% 
  filter(!country_region %in% 'Others') %>% 
  group_by(country_region) %>% 
  summarise(total_active = sum(total_active)) %>% 
  filter(total_active > 0) %>% 
  mutate(log_total_confirmed = log(total_active)) -> countries

highchart() %>%
  hc_add_series_map(worldgeojson, countries, value = 'log_total_confirmed', joinBy = c('name','country_region'))  %>% 
  #hc_colors(c("darkorange", "darkgray")) %>% 
  hc_colorAxis(stops = color_stops()) %>% 
  hc_title(text = "Countries with nCov exposure") %>% 
  hc_subtitle(text = 'with Log of Total Active') 
```   


MAP
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------
hi!

```{r}

# library(htmltools)
df_open_line_list <- read.csv("data/COVID19_open_line_list.csv", encoding = "UTF-8" , stringsAsFactors = FALSE)

df_open_line_list$date = as.Date(df_open_line_list$date_confirmation, format = "%d.%m.%y")

# Extract dates
all_dates <- df_open_line_list$date %>% 
  na.omit() %>% 
  unique() %>% 
  as.POSIXct(origin = "1970-01-01")

# str(df_open_line_list)

df_map = df_open_line_list %>% 
  select(date, city, latitude, longitude)
# %>% filter(!is.na(longitude) & !is.na(latitude) & !is.na(date))


df_map$latitude[df_map$latitude == "#N/A"] <- NA
df_map$longitude[df_map$longitude == "#N/A"] <- NA
df_map = df_map[!is.na(df_map$latitude),]
df_map = df_map[!is.na(df_map$longitude),]
# df_open_line_list$longitude[654]
# is.na(df_open_line_list$longitude[654])

df_map$longitude = as.double(df_map$longitude)
df_map$latitude = as.double(df_map$latitude)
# class(df_map$latitude)
# class(df_map$longitude)
df_map = df_map %>% 
  filter(longitude %inrange% range(-180:180) & latitude %inrange% range(-90:90)) %>%
  group_by(date, city, longitude, latitude) %>% 
  summarise(n = n()*1)

# colorpal = colorNumeric("BrBG", df_map$n)

# Calculate some basics
only_numeric <- sort(as.numeric(unique(df_map$n)))

col_pal <- colorNumeric(
    c(rep("#FFFFFF", 1), viridisLite::viridis(99)),
    domain = c(min(only_numeric, na.rm = TRUE), max(only_numeric, na.rm = T))
  )

max_val <- max(only_numeric, na.rm = T)
# Create Date input

sliderInput(inputId = "datum", 
            min = min(all_dates), max = max(all_dates), value = min(all_dates), 
label = "Select mapping date: ", 
timeFormat="%Y-%m-%d", 
animate=animationOptions(interval = 3000, loop = FALSE))

# Extract the current date
# curr_date <- reactiveVal( as.character(Sys.Date() + 1))
```


Column 
-----------------------------------------------------------------------

### 
```{r}

renderLeaflet(
df_map %>%
  filter(date == as.character(input$datum)) %>%
  select(date, city, latitude, longitude, n) %>%
  filter(n > 0) %>%
  # mutate(active_scaled = case_when(
  #       as.Date(input$datum, origin = "1970-01-01") > as.Date(Last_update_date, origin = "1970-01-01") ~ scales::rescale(
  #         x = n, from = c(0, max_val), to = c(12000, 650000)
  #       ),
  #     TRUE ~ scales::rescale(x = n, from = c(0, max_val), to = c(60000, 450000))
  #   ),
  #   text = paste0(n),
  #   color = col_pal(n)
  #   ) %>%
    arrange(n) %>%
  leaflet() %>%
  addTiles() %>%
  setView(0,20,1.5) %>%
  addCircleMarkers(lng = ~longitude, lat = ~latitude, weight = 1, radius = ~n, label = ~city, fillColor = ~ col_pal)
)




```




Other
=======================================================================

Column {.tabset}
-------------------------------------

### Worldwide COVID-19 spread

```{r}
library(tidyverse)
library(reshape2)
library(purrrlyr)

# download dataset
df <- read_csv(url('https://covid.ourworldindata.org/data/ecdc/full_data.csv'))

# normalization function
fun_normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# preprocess data
df_prep <- df %>%
  filter(location != 'World') %>%
  
  group_by(location) %>%
  # remove earlier dates
  filter(date > as.Date('2020-01-15', format = '%Y-%m-%d')) %>%
  # remove coutries with less than 1000 total cases
  filter(max(total_cases) > 1000) %>%
  # replace negative values with the mean 
  mutate(new_cases = ifelse(new_cases < 0,
                            round((lag(new_cases, default = 0) + lead(new_cases, default = 0)) / 2),
                            new_cases)) %>%
  ungroup() %>%
  select(location, date, new_cases) %>%
  # prepare data for normalization
  dcast(., date ~ location, value.var = 'new_cases') %>%
  # replace NAs with 0
  dmap_at(c(2:ncol(.)), function(x) ifelse(is.na(x), 0, x)) %>%
  # normalization
  dmap_at(c(2:ncol(.)), function(x) fun_normalize(x)) %>%
  melt(., id.vars = c('date'), variable.name = 'country') %>%
  mutate(value = round(value, 6))


# define countries order for plots
country_ord_1 <- df_prep %>%
  group_by(country) %>%
  filter(value == 1) %>%
  ungroup() %>%
  arrange(date, country) %>%
  distinct(country) %>%
  mutate(is_odd = ifelse((row_number() - 1) %% 2 == 0, TRUE, FALSE))

country_ord_anim <- bind_rows(country_ord_1 %>%
                                filter(is_odd == TRUE) %>%
                                arrange(desc(row_number())),
                              country_ord_1 %>%
                                filter(is_odd == FALSE))

# data for animated plot
df_plot_anim <- df_prep %>%
  mutate(country = factor(country, levels = c(as.character(country_ord_anim$country)))) %>%
  group_by(country) %>%
  mutate(first_date = min(date[value >= 0.03])) %>%
  mutate(cust_label = ifelse(date >= first_date, as.character(country), '')) %>%
  ungroup()


# color palette
cols <- c('#e7f0fa','#c9e2f6', '#95cbee', '#0099dc', '#4ab04a', '#ffd73e', '#eec73a', '#e29421', '#e29421', '#f05336', '#ce472e')


# Animated Heatmap plot
p <- ggplot(df_plot_anim, aes(y = country, x = date, fill = value)) +
  theme_minimal() +
  geom_tile(color = 'white', width = .9, height = .9) +
  scale_fill_gradientn(colours = cols, limits = c(0, 1),
                       breaks = c(0, 1),
                       labels = c('0', 'max'),
                       guide = guide_colourbar(ticks = T, nbin = 50, barheight = .5, label = T, barwidth = 20)) +
  
  geom_text(aes(x = first_date, label = cust_label), size = 3, color = '#797D7F') +
  scale_y_discrete(position = 'right') +
  coord_equal() +
  
  theme(legend.position = 'bottom',
        legend.direction = 'horizontal',
        plot.title = element_text(size = 20, face = 'bold', vjust = 2, hjust = 0.5),
        axis.text.x = element_text(size = 8, hjust = .5, vjust = .5, face = 'plain'),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
  ) +
  ggtitle('Worldwide COVID-19 spread: new daily cases normalized to location maximum')


# animated chart
library(gganimate)
library(gifski)

anim <- p + 
  transition_components(date) +
  ggtitle('Worldwide COVID-19 spread: new daily cases normalized to location maximum',
          subtitle = 'Date {frame_time}') +
  shadow_mark()

animate(anim,
        nframes = as.numeric(difftime(max(df_plot_anim$date), min(df_plot_anim$date), units = 'days')) + 1,
        duration = 12,
        fps = 12,
        width = 1200,
        height = 840,
        start_pause = 5,
        end_pause = 25,
        renderer = gifski_renderer())
# anim_save('covid-19.gif')

```


<!-- ### plot -->

```{r}

# # Heatmap plot 1
# df_plot_1 <- df_prep %>%
#   mutate(country = factor(country, levels = c(as.character(country_ord_1$country)))) %>%
#   group_by(country) %>%
#   mutate(first_date = min(date[value >= 0.03])) %>%
#   ungroup()
# 
# ggplot(df_plot_1, aes(y = country, x = date, fill = value)) +
#   theme_minimal() +
#   geom_tile(color = 'white', width = .9, height = .9) +
#   scale_fill_gradientn(colours = cols, limits = c(0, 1),
#                        breaks = c(0, 1),
#                        labels = c('0', 'max'),
#                        guide = guide_colourbar(ticks = T, nbin = 50, barheight = .5, label = T, barwidth = 10)) +
#   
#   geom_text(aes(x = first_date, label = country), size = 3, color = '#797D7F') +
#   scale_y_discrete(position = 'right') +
#   coord_equal() +
#   
#   theme(legend.position = 'bottom',
#         legend.direction = 'horizontal',
#         plot.title = element_text(size = 8, face = 'bold', vjust = 2, hjust = 0.5),
#         axis.text.x = element_text(size = 8, hjust = .5, vjust = .5, face = 'plain'),
#         axis.text.y = element_text(size = 6, hjust = .5, vjust = .5, face = 'plain'),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank()
#   ) +
#   ggtitle('Worldwide COVID-19 spread: new daily cases normalized to location maximum')


# Heatmap plot 2
# df_plot_2 <- df_prep %>%
#   group_by(country) %>%
#   filter(date >= min(date[value > 0])) %>%
#   arrange(date, .by_group = TRUE) %>%
#   mutate(centr_day = min(row_number()[value == 1]),
#          n_day = row_number() - centr_day) %>%
#   ungroup()
# 
# country_ord_2 <- df_plot_2 %>%
#   group_by(country) %>%
#   filter(date >= min(date[value == 1])) %>%
#   summarise(value = sum(value)) %>%
#   ungroup() %>%
#   arrange(value, country) %>%
#   distinct(country)
# 
# df_plot_2 <- df_plot_2 %>%
#   mutate(country = factor(country, levels = c(as.character(country_ord_2$country)))) %>%
#   group_by(country) %>%
#   mutate(first_date = min(n_day[value >= 0.01])) %>%
#   ungroup()

```

#### Comparison of different countries

```{r}

# # Heatmap plot 2
# ggplot(df_plot_2, aes(y = country, x = n_day, fill = value)) +
#   theme_minimal() +
#   geom_tile(color = 'white', width = .9, height = .9) +
#   scale_fill_gradientn(colours = cols, limits = c(0, 1),
#                        breaks = c(0, 1),
#                        labels = c('0', 'max'),
#                        guide = guide_colourbar(ticks = T, nbin = 50, barheight = .5, label = T, barwidth = 10)) +
#   
#   geom_text(aes(x = first_date, label = country), size = 3, color = '#797D7F') +
#   coord_equal() +
#   
#   theme(legend.position = 'bottom',
#         legend.direction = 'horizontal',
#         plot.title = element_text(size = 8, face = 'bold', vjust = 2, hjust = 0.5),
#         axis.text.x = element_text(size = 8, hjust = .5, vjust = .5, face = 'plain'),
#         #axis.text.y = element_text(size = 6, hjust = .5, vjust = .5, face = 'plain'),
#         axis.text.y = element_blank(),
#         axis.title.y = element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank()
#   ) +
#   ggtitle('Comparison of different countries effectiveness against COVID-19 
#                 (new daily cases normalized to location maximum and data centered on a day with maximum new cases)')
```

### plot




<!-- Column {.sidebar} -->
<!-- ----------------------------------------------------------------------- -->
<!-- hi! -->

<!-- Column  -->
<!-- ----------------------------------------------------------------------- -->




<!-- Interactive Plot  -->
<!-- ======================================================================= -->

<!-- Column {.sidebar} -->
<!-- ----------------------------------------------------------------------- -->
<!-- hi! -->


Data Intro 
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------
-- covid_19_data

* observation_date ：mm / date / yyyy
* Province/State：
* Country/Region：
* confirmed：
* Deaths：
* recovered：

```{r}
# # value is always yyyy-mm-date, even if the display format is different
dateInput('start_date',
      label = 'Date Start: mm/dd/yyyy',
      value = as.character(Sys.Date()),
      format = "mm/dd/yyyy"
    )

selectInput("Country", "Select Country/Region:", choices = country_list, multiple = FALSE)

```



row 
-----------------------------------------------------------------------

```{r}
# raw data 
DT::renderDataTable({
  output_data <- covid_19_data[covid_19_data$date >= input$start_date,]
  output_data <- output_data[output_data$country_region == input$Country,]
  DT::datatable(output_data, options = list(
    pageLength = 25
  ))
})

```


